Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2023-09-25 analysis/paper/paper.qmd
minor edit for the submission and add submission materials
Created jpg version of figure for submission.

# ggsave(here::here("analysis/figures/fig-map.png"),
#        width = 4,
#        height = 4.5,
#        units = "in")
```

@@

# ggsave(here::here("analysis/figures/fig-tcsa-all-sp.png"),
#        width = 4.45,
#        height = 4.5,
#        units = "in")

@@

# ggsave(here::here("analysis/figures/fig-artifact-size-cluster.png"),
#        width = 4,
#        height = 4,
#        units = "in")

@@

# ggsave(here::here("analysis/figures/fig-tcsa-raw-materials.png"),
#        width = 4.3,
#        height = 2.7,
#        units = "in",
#        bg = "white")
```

@@

# ggsave(here::here("analysis/figures/fig-tcsa-size.png"),
#        width = 4,
#        height = 3.3,
#        units = "in")

@@

# ggsave(here::here("analysis/figures/fig-tcsa-radio-carbon.png"),
#        width = 4,
#        height = 4.5,
#        units = "in",
#        bg = "white")

@@

# ggsave(here::here("analysis/figures/fig-tcsa-per-sites.png"),
#        width = 4.3,
#        height = 3,
#        units = "in",
#        bg = "white")
```

@@

# ggsave(here::here("analysis/figures/fig-gis-tcsa-sitess.png"),
#        width = 4,
#        height = 6,
#        units = "in",
#        bg = "white")

@@

<!-- The following line inserts a page break  -->

>>>>

# ggsave(here::here("analysis/figures/fig-map.jpg"),
#        width = 4,
#        height = 4.5,
#        units = "in",
#        dpi = 400)
```

@@

# ggsave(here::here("analysis/figures/fig-tcsa-all-sp.jpg"),
#        width = 4.45,
#        height = 4.5,
#        units = "in",
#        dpi = 400)

@@

# ggsave(here::here("analysis/figures/fig-artifact-size-cluster.jpg"),
#        width = 4,
#        height = 4,
#        units = "in",
#        dpi = 400)

@@

# ggsave(here::here("analysis/figures/fig-tcsa-raw-materials.jpg"),
#        width = 4.3,
#        height = 2.7,
#        units = "in",
#        bg = "white",
#        dpi = 400)
```

@@

# ggsave(here::here("analysis/figures/fig-tcsa-size.jpg"),
#        width = 4,
#        height = 3.3,
#        units = "in",
#        dpi = 400)

@@

# ggsave(here::here("analysis/figures/fig-tcsa-radio-carbon.jpg"),
#        width = 4,
#        height = 4.5,
#        units = "in",
#        bg = "white",
#        dpi = 400)

@@

# ggsave(here::here("analysis/figures/fig-tcsa-per-sites.jpg"),
#        width = 4.3,
#        height = 3,
#        units = "in",
#        bg = "white",
#        dpi = 400)
```

@@

# ggsave(here::here("analysis/figures/fig-gis-tcsa-sitess.jpg"),
#        width = 4,
#        height = 6,
#        units = "in",
#        bg = "white",
#        dpi = 400)

@@

We are grateful for the insightful feedback provided on an early draft of this paper by Ben Fitzhugh and Peter Lape. Their valuable input greatly enhanced the quality of our work.
